---
title: "Five Parameters"
format: html
execute:
  echo: false
---

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
library(gtsummary)
```

```{r}
#| label: model
#| cache: true

df1 <- governors |>
select(last_name, year, state, sex, lived_after, election_age)

fit_all <- brm(data = df1, formula = lived_after ~ sex*election_age, silent = 2, refresh = 0, seed = 13)
```

```{r}
#| label: plot

ndata <- tibble(sex = c("Male", "Female"), 
       election_age = 50)

fit_all |>
add_epred_draws(newdata = ndata) |>
ggplot(aes(.epred, fill = sex)) +
geom_histogram(aes(y = after_stat(count/sum(count))),
alpha = 0.5, bins = 100, position = "identity") +
scale_x_continuous(labels = scales::number_format(accuracy = 1)) +
scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
labs(title = "Posterior for Expected Years Lived Post-Election",
subtitle = "Male candidates live longer",
x = "Years",
y = "Probability")
```

Using data from deceased United States gubernatorial candidates between 1945 and 2012, we seek to predict the post-election longevity of candidates in state-wide races. There is concern that there are longevity differences between major and minor party candidates. We are using a Bayesian regression model with the formula lived_after ~ sex * election_age, where lived_after represents post-election life expectancy. The model reveals that male candidates have longer longevity post-election than female candidates. Male candidates live 53 years longer than their female counterparts, with a 95% confidence interval of 9 and 97. However, we do not know the accuracy of our approximation for female candidates, as our data has fewer of them. 

$$ lived\_after_i =  \beta_0 + \beta_1 male_i + \beta_2 c\_election\_age_i + 
\\ \beta_3 male_i *  c\_election\_age_i + \epsilon_i $$

```{r}
tbl_regression(fit_all, intercept = TRUE)
```

